---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fediverser

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `fediverser` is to offer a client for the Fediverse that R users can customise: decide what is in front of them and why, not necessarily the most recent posts. 

At this stage, this is just a prototype. Install and run `fedi_app()` to see the little that works (show contents of a hashtag from an instance and get older posts with infinite scrolling but nothing more). 

It is built on modules, in a way that should eventually enable full functionalities (e.g. reply, favorite, etc.) from the app. 

Easy to toggle customisation could include:

- show just latest post by each user
- do not show again posts that I've already seen
- ...

## Installation

You can install the development version of `fediverser` from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("giocomai/fediverser")
```

## Example

Just run:

```{r eval = FALSE}
library("fediverser")
options(shiny.launch.browser = .rs.invokeShinyWindowExternal) 
fedi_app()
```

And you may get an idea of where this is going, obviously with more controls, better rendering of cards, etc. 

## Notes

Names of functions are subject to change, as they will likely have a common prefix such as `fedi_`

## Code of Conduct

Please note that the `fediverser` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
